---
title: "Map Assignment"
author: "Abdou K. Allayeh"
date: "10/9/2020"
output: html_document
---

# Introduction

The goal of this assignment is to create a web page using R Markdown that features a map created with Leaflet. The webpage should be hosted on either Github Pages, RPubs, or NeoCities. The webpage must also contain the date when the document was created.

# Submission
Here is the best 5 cities in Portugal to visit; Porto, Setubal, Braga, Lisbon and Corroios.

# Install Libraries

```{r}
library(knitr)
library(dplyr)
library(leaflet)
```

## Data collected from 
#  https://www.worldatlas.com/webimage/countrys/europe/pt.htm

## Read the Data

```{r}
A <- read.csv("~/RR-Project-1/Map Project/Locations in Portugal.csv")
A <- leaflet() %>%
  addTiles() %>%  
  addMarkers(lat=38.5244,lng=-8.8882, popup="Setubal", df$population) %>%
  addMarkers(lat=41.55032,lng=-8.42005, popup="Braga", df$population) %>%
  addMarkers(lat=41.14961,lng=-8.61099, popup="Porto", df$population) %>%
  addMarkers(lat=38.71667,lng=-9.13333, popup="Lisbon", df$population) %>%
  addMarkers(lat=38.64502,lng=-9.14843, popup="Corroios", df$population) %>%
  setView (lat=41.55032, lng=-8.42005, zoom=16) 
A
```
